% document type
\documentclass[landscape]{slides}

% euro/pt stuff
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{eurosym}

% graphs, links, videos, symbols...
\usepackage{graphicx}
\usepackage{epsfig,color}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{multimedia}
\usepackage{ifsym}
\usepackage{mdsymbol}

% Remove page numbers
\usepackage{nopageno}

% the actual presentation:
\author{Marcos Marado}
\title{git}
\date{February 2020}

\begin{document}

\begin{slide}
\maketitle
\end{slide}

\begin{slide}
\$ git init

\# this is a talk for git users, not for those who don't know git
\end{slide}

\begin{slide}
no central repository, no ``master of the truth''

\begin{itemize}
\item{} this includes your own repositories, gerrit, etc.
\item{} what is a repository? (master, origin/master)
\end{itemize}
\end{slide}

\begin{slide}
\begin{verbatim}
git push --force # AKA, I'm doing something wrong
\end{verbatim}
\end{slide}

\begin{slide}
commits vs. patches

\begin{itemize}
\item{} commits have commit messages, let's USE them!
	\begin{itemize}
	\item{} git log
	\end{itemize}
\item{} let's talk about git format-patch, git am, git ammend, git cherry-pick...
\item{} pick between projects
\item{} maintain commit's history!
\end{itemize}
\end{slide}

\begin{slide}
commits vs. tags

\begin{itemize}
\item{} change vs. code
\item{} branches vs. tags
\begin{itemize}
\item{} tip: do you want it to be mutable?
\end{itemize}
\end{itemize}
\end{slide}

\begin{slide}
commits have a parent...

\begin{itemize}
\item{} Changes have not: Change-Id
\item{} perfect for rebases (gerrit uses it for that all the time!)
\end{itemize}
\end{slide}

\begin{slide}
merge vs. rebase

\begin{small}
Merge:
\begin{verbatim}
git log --pretty=oneline
git log --graph --pretty=oneline
\end{verbatim}
\url{https://hackernoon.com/hn-images/0*NFscoCQwTuLB8mQu.png}
%%% (c) Tugberk Ugurlu -- http://www.tugberkugurlu.com/

Rebase: \\
\url{https://miro.medium.com/max/855/1*pzT4KMiZDOFsMOKH-cJjfQ.png} \\
%%% (c) Michael Aranda -- https://twitter.com/MichaelAranda0
\url{https://miro.medium.com/max/1204/1*bXetvZfHi78_SIWKYriZJw.png}
%%% (c) Alex Rock -- https://www.orbitale.io

\begin{itemize}
\item{} Use merge in cases where you want a set of commits to be clearly grouped together in history
\item{} Use rebase when you want to keep a linear commit history
\end{itemize}
\end{small}
\end{slide}

\begin{slide}
\begin{verbatim}
HEAD, HEAD~1
\end{verbatim}

\begin{small}
\begin{itemize}
	\item{} \url{http://marklodato.github.io/visual-git-guide/checkout-branch.svg}
	\item{} \url{http://marklodato.github.io/visual-git-guide/checkout-detached.svg}
\end{itemize}
%%% Copyright © 2010, Mark Lodato -- CC BY-NC-SA 3.0 USA -- https://github.com/MarkLodato/visual-git-guide
\end{small}
\end{slide}

\begin{slide}
squash!

\begin{verbatim}
git rebase -i HEAD~4
\end{verbatim}
\end{slide}

\begin{slide}
other git commands
\begin{verbatim}
git init
git clone (-b)
git add
git rm
git commit (-a, --amend, --date, --author...)
git pull
git push
git fetch # instead of a full git pull
git checkout (-b)
git branch (-a, -D)
git show
git diff (local changes, paths, between commits, branches...)
git grep
git archive
git log (commits, branches, tags, formats...)
git tag
git reset (--hard)
git blame
git bisect
\end{verbatim}
\end{slide}

\begin{slide}
other useful things

\begin{itemize}
\item{} .gitignore
\item{} pathogen
\end{itemize}
\end{slide}

\begin{slide}
\begin{center}
\begin{Huge}
Questions?
\end{Huge}
\end{center}
\end{slide}

\end{document}
